Do music charts still matter in the streaming age? An analysis predicting Beyoncé’s Spotify numbers using a regression model.

### 2024-04-18 paper/paper.qmd
Add completed references to paper

To visualize our data, we create a table and graph. @tbl-variables shows a sample of the dataset with all the variables and the first 10 out of 140 observations. Furthermore, @fig-variables show a scatterplot of the data with all 140 observations. We see a positive correlation between the number of Spotify streams and weeks spent on the *Billboard Hot 100*.

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: tbl-variables
#| tbl-cap: "Sample of the cleaned dataset with the first 10 observations"

beyonce_cleaned |>
  slice(1:10) |>
  kable(
    col.names = c("Song", "Album", "Spotify Streams", "Weeks on Chart")
  )
```

@@

In the future, it could be on interest to run the analysis again to give Beyoncé’s latest album *COWBOY CARTER* more time to see how long it lasts on the chart. We could also standardize the length to accumulate streams such as one year after its release for consistency. Another possible idea for future work could be to use a mix of new and established artists to see if we get the same result.

>>>>

To visualize our data, we create a table and graph. @tbl-variables shows a sample of the dataset with all the variables and the first 5 out of 140 observations. Furthermore, @fig-variables show a scatterplot of the data with all 140 observations. We see a positive correlation between the number of Spotify streams and weeks spent on the *Billboard Hot 100*.

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: tbl-variables
#| tbl-cap: "Sample of the cleaned dataset with the first 5 observations"

beyonce_cleaned |>
  slice(1:5) |>
  kable(
    col.names = c("Song", "Album", "Spotify Streams", "Weeks on Chart")
  )
```

@@

In the future, it could be on interest to run the analysis again to give Beyoncé’s latest album, *COWBOY CARTER*, more time to see how long it lasts on the chart. We could also standardize the length to accumulate streams such as one year after its release for consistency. Another possible idea for future work could be to use a mix of new and established artists to see if we get the same result.
